How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-26 docs/PhysicsPaper/StokesErosion.tex
reading through paper and making small changes

\todo[inline]{Bryan left off here}

Instead of evaluating the Stokes double-layer potential~\eqref{eqn:velocityDLP} as a contour integral in $\RR^2$, we convert the integral to a sum of contour integrals around Jordan curves in $\CC$. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_2$ and use similar notation for $\yy$, $\nn$, and $\eeta$. We also interpret $\gamma$, the boundary of the $i^{th}$ grain or the bounding box $\Gamma$, as a Jordan curve in $\CC$. We introduce the functions
\begin{align}
  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)).
\end{align}
We then define the five Cauchy integrals
\begin{align}
  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\eta(y))}{x-y} \,dy, 
  \quad
  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Im(\eta(y))}{x-y} \, dy, 
  \quad
  v_3(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{Re(\overline{y}\eta(y))}{x-y} \, dy, \\
  v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
  \quad
  v_5(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_2(y)}{x-y} \, dy.
\end{align}
Then, the first and second components of the Stokes double-layer
potential are
\begin{subequations}
  \begin{align}
    u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
             \Re(v_3'(x)) + \Re(v_4(x)) \\
    u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
             \Im(v_3'(x)) + \Re(v_5(x)),
  \end{align}
  \label{eqn:velocityCauchy}
\end{subequations}
respectively. The components of the deformation tensor are
\begin{subequations}
  \begin{align}
    \pderiv{u_1}{x_1} &= -\Re(v'_1(x)) + \Re(v''_3(x)) + \Re(v'_4(x))
                         -\Re(x)\Re(v''_1(x)) - \Im(x)\Re(v''_2(x)) \\
    \pderiv{u_1}{x_2} &= -\Re(v'_2(x)) - \Im(v''_3(x)) - \Im(v'_4(x))
                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
    \pderiv{u_2}{x_1} &= +\Im(v'_1(x)) - \Im(v''_3(x)) + \Re(v'_5(x))
                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
    \pderiv{u_2}{x_2} &= +\Im(v'_2(x)) - \Re(v''_3(x)) - \Im(v'_5(x))
                         +\Re(x)\Re(v''_1(x)) + \Im(x)\Re(v''_2(x)) 
  \end{align}
  \label{eqn:deformationCauchy}
\end{subequations}
Having the deformation tensor at hand, the vorticity can be shown to
satisfy
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
     \Im(v_1'(x)) + \Re(v_2'(x)) + \Re(v_5'(x)) + \Im(v_4'(x)).
  \label{eqn:vorticityCauchy}
\end{align}
We note that the deformation tensor requires second-order derivatives of
Cauchy integrals, while the vorticity only requires first-order
derivatives.

@@

To approximate the Cauchy integrals and its
derivatives~\eqref{eqn:cauchy}, the trapezoid rule achieves spectral
accuracy. For example, the Cauchy integral~\eqref{eqn:cauchyv} can be
approximated as
\begin{align}
  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^{N} 
    w_j \frac{v^{-}(y_j)}{y_j - x},
  \label{eqn:trap}
\end{align}
where $y_j$ are equispaced points on $\gamma$, $w_j = L/N$, and $L$ is
the length of $\gamma$. Because the integrand is both periodic and
smooth, given a fixed point $x$, the trapezoid rule achieves spectral
accuracy~\cite{tre-wei2014}. However, for a fixed $N$, the quadrature
error is not bounded uniformly with respect to $x$ because the
derivative of the integrand grows without bound as $x$ approaches
$\gamma$. This error is problematic for many of our simulations since we
allow for eroding bodies to be arbitrarily close to one another, and we
often compute the velocity and vorticity at points in the fluid domain
that are close to an eroding body. In contrast to the integrand in the
Cauchy integral~\eqref{eqn:cauchyv}, the integrand in the identity
\begin{align}
  \frac{1}{2\pi i}\int_{\gamma} 
    \frac{v^{-}(y) - v(x)}{y-x} \, dy = 0, \quad x \in \Omega,
  \label{eqn:trap2}
\end{align}
is bounded with respect to $x$, and therefore the error of the trapezoid
rule is bounded with respect to $x$. Applying the trapezoid rule, we
have
\begin{align}
  \frac{1}{2\pi i}\sum_{j=1}^{N} w_{j} 
    \frac{v^{-}(y_j) - v(x)}{y_j - x} \approx 0,
\end{align}
where the error is now uniformly bounded for all $x$. Rearranging, we
have
\begin{align}
  v(x) \approx \left(\frac{1}{2\pi i}\sum_{j=1}^N 
    \frac{v^{-}(y_j)}{y_j - x} w_j \right) \Bigg/
  \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j - x} w_j \right), 
  \quad x \in \Omega.
  \label{eqn:vBary}
\end{align}
Note that the numerator in~\eqref{eqn:vBary} is identical to
equation~\eqref{eqn:trap}, while the denominator is an approximation of
the analytic function $v(x) = 1$. As $x$ approaches $\gamma$, the errors
in the numerator and denominator grow, however, since the integrand in
equation~\eqref{eqn:trap2} is bounded independent of $x$, the error of
the ratio is bounded independent of $x$.

The derivatives of the Cauchy integral in~\eqref{eqn:cauchy} can be
approximated with similar quadrature rules. For $x \in \Omega$, 
\begin{align}
  v'(x) &\approx \left(\frac{1}{2\pi i}\sum_{j=1}^{N}
    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j \right)
  \Bigg/
  \left(\frac{1}{2\pi i}\sum_{j=1}^{N} \frac{1}{y_j-x} w_j\right), 
  \label{eqn:D1vBary} \\
  v''(x) &\approx \left(\frac{2}{2\pi i}\sum_{j=1}^N 
    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j \right)
    \Bigg/
    \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j-x}w_j\right),
  \label{eqn:D2vBary}
\end{align}
where the quadrature rule is spectrally accurate and the error is
independent of $x$. We note that
equations~\eqref{eqn:vBary},~\eqref{eqn:D1vBary},
and~\eqref{eqn:D2vBary} all assume that $x \in \Omega$, where $\Omega$
is the bounded region interior to the Jordan curve $\gamma$. However, in
our application, when $\gamma$ is one of the eroding bodies, $x$ is in
the exterior region of the Jordan curve. In this case, slightly
different identities are used, but they all guarantee that the trapezoid
rule achieves spectral accuracy with an error that is independent of
$x$. A complete description of the quadrature rules
for~\eqref{eqn:vBary} and~\eqref{eqn:D1vBary} are described by Barnett,
Wu, and Veerapaneni~\cite{bar-wu-vee2015}, and the quadrature rule
for~\eqref{eqn:D2vBary} is described in our previous
work~\cite{chiu2020viscous}.

@@

%-----------------------------------------------------------------------------------------------%
%\subsection{Boundary Integral Representation in $\RR^2$}
%-----------------------------------------------------------------------------------------------%

%
%Once~\eqref{eqn:BIE} is solved for the density function $\eeta$, the
%corresponding deformation tensor, pressure, and vorticity at $\xx \in
%\Omega$ are written in terms of layer potentials~\citep{qua-moo2018}.
%To compute the deformation tensor for $\xx \in \gamma$, we include the
%jump term
%\begin{align}
%  \frac{1}{2} \left(\pderiv{\eeta}{\ss} \cdot \ss \right) \left[
%    \begin{array}{cc}
%      s_x^2 - s_y^2 & 2s_x s_y \\ 2s_x s_y & s_y^2 - s_x^2
%    \end{array}
%  \right].
%  \label{eqn:deformationJump}
%\end{align}
%Finally, the deformation tensor, pressure, and vorticity due to the
%Stokeslets and rotlets are readily available~\citep{poz1992}. Having
%computed the deformation tensor on $\gamma$, the shear stress is
%computed using equation~\eqref{tau0}.

%%-----------------------------------------------------------------------------------------------%
%\subsection{Cauchy Integral Formulation}
%\label{sec:DLPcomplex}
%%-----------------------------------------------------------------------------------------------%
%The velocity double-layer potential~\eqref{eqn:velocityDLP}, and its
%corresponding deformation tensor, pressure, and vorticity are all
%written as layer potentials in $\RR^2$. However, the quadrature method
%we introduce in section~\ref{sec:method} requires complex-valued
%representations. The first step to form a complex representation is to
%write the Laplace double-layer potential as the complex integral
%\begin{align}
%  \DD[\eeta](\xx) = \frac{1}{2\pi} \int_{\bd\Omega} 
%    \frac{\rr \cdot \nn}{\rho^2}\eeta(\yy)\, ds_\yy = \Real (v(x)),
%\end{align}
%where
%\begin{align}
%  v(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
%    \frac{\eta(y)}{x - y} \, dy, \quad x \in \Omega.
%  \label{eqn:laplaceComplex}
%\end{align}
%Here $x = x_1 + i x_2,y = y_1 + i y_2 \in \CC$ are the complex
%counterparts of $\xx = (x_1,x_2),\yy = (y_1,y_2) \in \RR^2$, and $\eta =
%\eta_1 + i \eta_2$ is the complex counterpart of $\eeta =
%(\eta_1,\eta_2)$. Therefore, depending on the formulation of the layer
%potential, $\Omega$ is interpreted as a subset of $\RR^2$ or $\CC$.
%Equation~\eqref{eqn:laplaceComplex} is converted to a Cauchy integral by
%first finding the boundary data of $v$. If $\Omega$ is a
%simply-connected interior domain, then the boundary data of $v$
%satisfies the Sokhotski-Plemelj jump relation
%\begin{align}
%  \label{eqn:SPrelation}
%  v(x) = - \frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
%    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
%\end{align}
%For exterior domains, the jump term changes from $-1/2$ to $1/2$, and
%for multiply-connected domains, such as a porous media, $\bd\Omega$ is
%decomposed into its different connected components and the appropriate
%jump relation is applied.  Having computed the boundary data of the
%holomorphic function $v$, by the Cauchy integral theorem we have
%\begin{subequations}
%  \label{eqn:cauchy}
%  \begin{alignat}{3}
%  v(x) &= \frac{1}{2\pi i}\int_{\bd\Omega} 
%    \frac{v(y)}{y-x} \,dy, \\
%  v'(x) &= \frac{1}{2\pi i} \int_{\bd\Omega}
%    \frac{v(y)}{(y-x)^2} \, dy, \\
%  v''(x) &= \frac{1}{\pi i} \int_{\bd\Omega}
%    \frac{v(y)}{(y-x)^3} \, dy,
%  \end{alignat}
%\end{subequations}
%for $x \in \Omega$.  Since $v(x)$ depends on the complex-valued density
%function $\eta$, we use the notation $v[\eta](x)$ for the holomorphic
%function defined in equation~\eqref{eqn:laplaceComplex}, and its first
%two derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.  
%  
%Finally, the Stokes double-layer potential~\eqref{eqn:velocityDLP} can
%be written using a Laplace double-layer
%potential~\eqref{eqn:laplaceComplex} and its gradients 
%\begin{equation}
%  \label{eqn:Stokes2Laplace}
%  \begin{aligned}
%    \DDD[\eeta](\xx) &= 
%      \frac{1}{2\pi} \int_{\bd\Omega} 
%        \frac{\nn}{\rho^2} (\rr \cdot \eeta) \, ds_\yy + 
%      \frac{1}{2\pi} \nabla \int_{\bd\Omega}
%        \frac{\rr \cdot \nn}{\rho^2} (\yy \cdot \eeta) \, ds_\yy \\
%      &- \frac{1}{2\pi} x_1 \nabla \int_{\bd\Omega}
%        \frac{\rr \cdot \nn}{\rho^2}\eta_1(\yy) \, ds_\yy -
%      \frac{1}{2\pi} x_2 \nabla \int_{\bd\Omega}
%        \frac{\rr \cdot \nn}{\rho^2}\eta_2(\yy) \, ds_\yy.
%  \end{aligned}
%\end{equation}
%Therefore, the Stokes double-layer potential can be written as a sum of
%Cauchy integrals and its first derivative~\citep{bar-wu-vee2015}
%\begin{equation}
%  \begin{aligned}
%    u_1(x) &= \Real (v[\psi_1](x)) + \Real (v'[y\cdot\eta](x)) 
%             -x_1\Real (v'[\eta_1](x)) - x_2\Real (v'[\eta_2](x)), \\
%    u_2(x) &= \Real (v[\psi_2](x)) - \Imag (v'[y\cdot\eta](x)) 
%         +x_1\Imag (v'[\eta_1](x)) + x_2\Imag (v'[\eta_2](x)),
%  \end{aligned}
%  \label{eqn:cauchyVelocity}
%\end{equation}
%where $y \cdot \eta = y_1 \eta_1 + y_2 \eta_2$, 
%\begin{align} 
%  \psi_1=(\eta_1+i\eta_2)\frac{\Real(n)}{n}, \quad
%  \psi_2=(\eta_1+i\eta_2)\frac{\Imag(n)}{n},
%\end{align}
%and $n \in \CC$ is the complex counterpart of the outward unit normal
%$\nn \in \RR^2$.
%
%%-----------------------------------------------------------------------------------------------%
%\subsection{Cauchy Integral Representation for the Gradient of the
%Double-Layer Potential}
%\label{sec:gradDLPcomplex}
%%-----------------------------------------------------------------------------------------------%
%Computing the shear stress and vorticity requires a complex-valued layer
%potential representation of the velocity gradient.  The deformation
%tensor at $x \in \Omega$ is found by computing the derivatives of the
%expressions for $u_1$ and $u_2$ in equation~\eqref{eqn:cauchyVelocity}  
%\begin{equation}
%\label{eqn:cauchyGradient}
%  \begin{aligned}
%    \pderiv{u_1}{x_1} &= +\Real (v'[\psi_1](x)) + 
%    \Real (v''[y\cdot\eta](x)) - \Real (v'[\eta_1](x)) \\
%    &- x_1\Real (v''[\eta_1](x)) - x_2\Real (v''[\eta_2](x)), \\
%    \pderiv{u_1}{x_2} &= - \Imag (v'[\psi_1](x)) - 
%    \Imag (v''[y\cdot\eta](x)) + x_1\Imag (v''[\eta_1](x)) \\
%    &- \Real (v'[\eta_2](x)) + x_2\Imag (v''[\eta_2](x)), \\
%    \pderiv{u_2}{x_1} &= +\Real (v'[\psi_2](x)) - 
%    \Imag (v''[y\cdot\eta](x)) + \Imag (v'[\eta_1](x))  \\
%    &+ x_1\Imag (v''[\eta_1](x)) + x_2\Imag (v''[\eta_2](x)), \\
%    \pderiv{u_2}{x_2} &= -\Imag (v'[\psi_2](x)) - 
%    \Real (v''[y\cdot\eta](x)) + x_1\Real (v''[\eta_1](x)) \\
%    &+ \Imag (v'[\eta_2](x)) + x_2\Real (v''[\eta_2](x)).
%  \end{aligned}
%\end{equation}
%The same expressions are used to compute the deformation tensor for $x
%\in \bd\Omega$, except that the jump
%condition~\eqref{eqn:deformationJump} is included.  Finally, to compute
%the shear stress, the deformation tensor on $\bd\Omega$ is applied to
%the normal and tangent vectors as in equation~\eqref{tau0}.
%The velocity gradient is also used to compute the vorticity in the fluid
%bulk.  For $x \in \Omega$, the Cauchy integral representation of the
%vorticity at $x \in \Omega$ is
%\begin{align}
%  \omega(x) = 
%    \Real (v'[\psi_2](x)) + \Imag (v'[\psi_1](x))+ 
%    \Real (v'[\eta_2](x))+ \Imag (v'[\eta_1](x)).
%\end{align}

>>>>

Instead of evaluating the Stokes double-layer potential~\eqref{eqn:velocityDLP} as a contour integral in $\RR^2$, we convert the integral to a sum of contour integrals around Jordan curves in $\CC$. We identify $\xx = (x_1,x_2)$ with $x = x_1 + ix_2$ and use similar notation for $\yy$, $\nn$, and $\eeta$. We also interpret $\gamma$, the boundary of the $i^{th}$ grain or the bounding box $\Gamma$, as a Jordan curve in $\CC$. We introduce the functions
\begin{align}
  \tau_1(y) = \eta(y) \overline{n(y)} \Re(n(y)), \quad 
  \tau_2(y) = \eta(y) \overline{n(y)} \Im(n(y)),
\end{align}
and then define the five Cauchy integrals
\begin{align}
  v_1(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\Re(\eta(y))}{x-y} \,dy, 
  \quad
  v_2(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\Im(\eta(y))}{x-y} \, dy, 
  \quad
  v_3(x) = \frac{1}{2\pi i} \int_{\gamma}
  \frac{\Re(\overline{y}\eta(y))}{x-y} \, dy, \\
  v_4(x) &= \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_1(y)}{x-y} \, dy,
  \quad
  v_5(x) = \frac{1}{2\pi i} \int_{\gamma} \frac{\tau_2(y)}{x-y} \, dy.
\end{align}
Then, the first and second components of the Stokes double-layer
potential are
\begin{subequations}
  \begin{align}
    u_1(x) &= -\Re(x)\Re(v_1'(x)) - \Im(x)\Re(v_2'(x)) + 
             \Re(v_3'(x)) + \Re(v_4(x)) \\
    u_2(x) &= +\Re(x)\Im(v_1'(x)) + \Im(x)\Im(v_2'(x)) - 
             \Im(v_3'(x)) + \Re(v_5(x)),
  \end{align}
  \label{eqn:velocityCauchy}
\end{subequations}
respectively. The components of the deformation tensor are
\begin{subequations}
  \begin{align}
    \pderiv{u_1}{x_1} &= -\Re(v'_1(x)) + \Re(v''_3(x)) + \Re(v'_4(x))
                         -\Re(x)\Re(v''_1(x)) - \Im(x)\Re(v''_2(x)) \\
    \pderiv{u_1}{x_2} &= -\Re(v'_2(x)) - \Im(v''_3(x)) - \Im(v'_4(x))
                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
    \pderiv{u_2}{x_1} &= +\Im(v'_1(x)) - \Im(v''_3(x)) + \Re(v'_5(x))
                         +\Re(x)\Im(v''_1(x)) + \Im(x)\Im(v''_2(x)) \\
    \pderiv{u_2}{x_2} &= +\Im(v'_2(x)) - \Re(v''_3(x)) - \Im(v'_5(x))
                         +\Re(x)\Re(v''_1(x)) + \Im(x)\Re(v''_2(x)) 
  \end{align}
  \label{eqn:deformationCauchy}
\end{subequations}
Having the deformation tensor at hand, the vorticity can be shown to
satisfy
\begin{align}
  \omega(x) = \pderiv{u_2}{x_1} - \pderiv{u_1}{x_2} = 
     \Im(v_1'(x)) + \Re(v_2'(x)) + \Re(v_5'(x)) + \Im(v_4'(x)).
  \label{eqn:vorticityCauchy}
\end{align}
We note that the deformation tensor requires second-order derivatives of
Cauchy integrals, while the vorticity only requires first-order
derivatives.

@@

The trapezoid rule can be used to approximate this Cauchy integral and
its derivatives. For example, the Cauchy integral~\eqref{eqn:cauchyv}
can be approximated as
\begin{align}
  v(x) \approx \frac{1}{2\pi i} \sum_{j=1}^{N} 
    w_j \frac{v^{-}(y_j)}{y_j - x},
  \label{eqn:trap}
\end{align}
where $y_j$ are equispaced points on $\gamma$, $w_j = L/N$, and $L$ is
the length of $\gamma$. Because the integrand is both periodic and
smooth, given a fixed point $x$, the trapezoid rule achieves spectral
accuracy~\cite{tre-wei2014}. However, for a fixed $N$, the quadrature
error is not bounded uniformly with respect to $x$ because the
derivative of the integrand grows without bound as $x$ approaches
$\gamma$. This error is problematic for many of our simulations since we
allow eroding bodies to be arbitrarily close to one another, and we
often compute the velocity and vorticity at points in the fluid domain
that are close to an eroding body. In contrast to the integrand in the
Cauchy integral~\eqref{eqn:cauchyv}, the integrand in the identity
\begin{align}
  \frac{1}{2\pi i}\int_{\gamma} 
    \frac{v^{-}(y) - v(x)}{y-x} \, dy = 0, \quad x \in \Omega,
  \label{eqn:trap2}
\end{align}
is bounded with respect to $x$, and therefore the error of the trapezoid
rule is bounded with respect to $x$. Applying the trapezoid rule, we
have
\begin{align}
  \frac{1}{2\pi i}\sum_{j=1}^{N} w_{j} 
    \frac{v^{-}(y_j) - v(x)}{y_j - x} \approx 0,
\end{align}
where the error is now uniformly bounded for all $x$. Rearranging, we
have
\begin{align}
  v(x) \approx \left(\frac{1}{2\pi i}\sum_{j=1}^N 
    \frac{v^{-}(y_j)}{y_j - x} w_j \right) \Bigg/
  \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j - x} w_j \right), 
  \quad x \in \Omega.
  \label{eqn:vBary}
\end{align}
Note that the numerator in~\eqref{eqn:vBary} is identical to
equation~\eqref{eqn:trap}, while the denominator is an approximation of
the analytic function $v(x) = 1$. As $x$ approaches $\gamma$, the errors
in the numerator and denominator grow, however, since the integrand in
equation~\eqref{eqn:trap2} is bounded independent of $x$, the error of
the ratio is bounded independent of $x$.

The derivatives of the Cauchy integral in~\eqref{eqn:cauchy} can be
approximated with a uniformly spectral error using similar quadrature
rules. For $x \in \Omega$, 
\begin{align}
  v'(x) &\approx \left(\frac{1}{2\pi i}\sum_{j=1}^{N}
    \frac{v^{-}(y_j) - v(x)}{(y_j-x)^2} w_j \right)
  \Bigg/
  \left(\frac{1}{2\pi i}\sum_{j=1}^{N} \frac{1}{y_j-x} w_j\right), 
  \label{eqn:D1vBary} \\
  v''(x) &\approx \left(\frac{2}{2\pi i}\sum_{j=1}^N 
    \frac{v^{-}_{j} - v(x) - (y_j-x)v'(x)}{(y_j-x)^3}w_j \right)
    \Bigg/
    \left(\frac{1}{2\pi i}\sum_{j=1}^N \frac{1}{y_j-x}w_j\right).
  \label{eqn:D2vBary}
\end{align}
We note that equations~\eqref{eqn:vBary},~\eqref{eqn:D1vBary},
and~\eqref{eqn:D2vBary} all assume that $x \in \Omega$, where $\Omega$
is the bounded region interior to the Jordan curve $\gamma$. However, in
our application, when $\gamma$ is one of the eroding bodies, $x$ is in
the exterior region of the Jordan curve. In this case, slightly
different identities are used, but they all guarantee that the trapezoid
rule achieves spectral accuracy with an error that is independent of
$x$. A complete description of the quadrature rules
for~\eqref{eqn:vBary} and~\eqref{eqn:D1vBary} are described by Barnett,
Wu, and Veerapaneni~\cite{bar-wu-vee2015}, and the quadrature rule
for~\eqref{eqn:D2vBary} is described in our previous
work~\cite{chiu2020viscous}.

@@
